---
title: 'Bio Stats II : Lab 1'
author: "Gavin Fay"
date: "01/27/2016"
output: beamer_presentation
---

## Lab schedule

__1/27: Introduction to R and R Studio, working with data__  
2/03: Intro to plotting, manipulating data  
2/10: Probability, linear modeling, PCA  
2/17: Programming practices, conditional statements  
2/24: Creating functions, debugging  
3/02: Permutation analysis  
3/09: Advanced plotting  

## Why R?

 __Reproducible__  
  - command line interface encourages organization  
  - scripts allow others (and you!) to reproduce analyses from end-to-end
 
 __Extensible__  
  - new methods delivered as developed  
  - continual expansion through new packages  
 
 __Open-source__  
  - all code can be examined by the user
  
 __Free__  
  - available to large set of users (and therefore developers)
 
 R is not the only solution out there.  
 The real goal is not to teach R, but concepts that all programming depends on.
 
***

Trevor Branch rule:  

### "Every analysis you do on a dataset will have to be redone 10–15 times before publication.  

###  Plan accordingly."


## Recommended reading

An introduction to R (Venables et al.)  
– <http://cran.r-project.org/doc/manuals/R-intro.pdf>

R reference card 2.0 (Baggott)  
– <http://cran.r-project.org/doc/contrib/Baggott-refcard-v2.pdf>  
– Extremely useful handout: put on wall in view of your desk  

There are many (many) R books out there. Good for reference.


## Installing R and R Studio

 __R__ (<http://r-project.org>)  
  - download appropriate version for your OS
 
 __R Studio__ (<http://rstudio.com>)  
  - a very good Integrated Development Environment (IDE) for R  
  provides:  
  - text editor  
  - syntax highlighting  
  - seamless code execution with R  
  
 You can use other text editors with R, but RStudio well organized.  
 (also looks same regardless of Operating System)
   

## Getting started, command line



## Getting Help

 R is a programming language, there is a learning curve.  

 Lots of resources:
 
 - help files  
 - online search results (Google 'Method X in R')
 - books
 - colleagues
 

## Resources


## Slide with R Code and Output

```{r}
summary(cars)
```

## Slide with Plot

```{r, echo=FALSE}
plot(cars)
```

## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.
